Integrative forecasting of seasonal influenza A/H3N2 by genotype and phenotype

### 2019-07-16 manuscript/supplement.tex

\subsection*{Simulations of A/H3N2-like populations}

@@

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/composite-model-accuracy-and-coefficients-for-simulated-populations.png}
  \caption{Composite model a) accuracy and b) coefficients for simulated populations of A/H3N2-like viruses.}
  \label{sup_fig:composite_model_accuracy_and_coefficients_for_simulated_populations}
  \end{center}
\end{figure*}

>>>>

@@

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/distance-of-simulated-populations-between-timepoints.png}
  \caption{Average weighted distance per year between simulated populations of viruses under the ``naive'' model.}
  \label{sup_fig:distance_of_simulated_populations_between_timepoints}
  \end{center}
\end{figure*}

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/unadjusted-composite-model-accuracy-and-coefficients-for-simulated-populations.png}
  \caption{Composite model a) accuracy and b) coefficients for simulated populations of A/H3N2-like viruses.}
  \label{sup_fig:unadjusted_composite_model_accuracy_and_coefficients_for_simulated_populations}
  \end{center}
\end{figure*}

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/distance-of-natural-populations-between-timepoints.png}
  \caption{Average weighted distance per year between natural populations of viruses under the ``naive'' model.}
  \label{sup_fig:distance_of_natural_populations_between_timepoints}
  \end{center}
\end{figure*}

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/unadjusted-composite-model-accuracy-and-coefficients-for-natural-populations.png}
  \caption{Composite model a) accuracy and b) coefficients for natural populations of A/H3N2 viruses.}
  \label{sup_fig:unadjusted_composite_model_accuracy_and_coefficients_for_natural_populations}
  \end{center}
\end{figure*}
